---
title: "Plant-pollinator Networks_Kaas_2018_&_2019"
output: html_notebook
---

*"Kaas 2018 & 2019: Plant-pollinator network"*

**Plotting overall flowering season: 2018 & 2019 combined**

1. Running libraries

```{r}
library(r2d3)
library(bipartite)
library(purrr) 
library(dplyr) 
library(tidyr) 
library(stringr)
library(tibble)
library(RColorBrewer)
library(bipartiteD3)
library(reshape2)
library(googlesheets4)
```

2. Load and read data

```{r}
#Read googlesheets
data_network <- read_sheet('https://docs.google.com/spreadsheets/URL_has_been_removed', sheet = 1)
```
3. Process data

```{r}

#My data set does not have the average of the visitation rate per unique plant-pollinator combination
#To take average visitation rate per unique plant-pollinator combination
library(plyr)

#Extracting the data I require for network analysis and calculating the mean visitation rate
#Extract data mentioning the column names and not numbers because later you may add or remove some

sub_data <- ddply(data_network, .(Flo_sp, Pollinator_type), summarize, mean=mean(visitation_rate_per_flower_per_hour, na.rm = TRUE))

#To find the rows in which pollinator type is NA. With '!' the places with NA will be marked as FALSE and not considered in data-set.
a <- !is.na(sub_data$Pollinator_type) 
sub_data_mean <- sub_data[a,]

#Added the column with WebID as KAAS for 130 rows as bipartite function requires WebID
WebID = c(rep("KAAS", 130))
sub_data_mean2 = cbind(sub_data_mean, WebID)

#using dcast function to convert long format to wide format, as plotweb function requires the data in short format
library(reshape2)
library(readr)

#I would use the data with removed NA values, and no webID, which is 'sub_data_mean'
#Function 'dcast': data.frame will be automatically converted to data.table, as is needed for plotweb function 
mydata_dcast <- dcast(sub_data_mean2, Flo_sp ~ Pollinator_type, value.var = "mean")

#Replacing all NA with zeros
mydata_dcast[is.na(mydata_dcast)] = 0

#Removing the 8th column as the column name is 'NA' with all 0 values
mydata_dcast = mydata_dcast[,-8]

row.names(mydata_dcast) <- mydata_dcast$Flo_sp

#Remove the first column
mydata_dcast = mydata_dcast[,-1]

#Round of the values to 1 decimal point
mydata_dcast2 = round(mydata_dcast, 1)

#removing the species that have all 0, that is, no visitation by any pollinator type
#subsetting the data as 'data_final'

data_final <- mydata_dcast2[rowSums(mydata_dcast2[])>0,]

```

4. Plotting the non-interactive network

```{r}
#To plot species as per your desired sequence, add them in a sequence inside a particular vector and mention it as 'seq.high' and 'seq.low' in plotweb function.

seq.low <- c("IsoLop","HabHey","ParCoe","PinCon","EriSed","PolChi","SmiBig","SmiHir","LinMys","ImpDal","SenBom","MurLan","MurBro","SopDel","RotFlo","DesRac","ImpTom","JusDif","ImpBal","ImpLaw","PogDec","UtrPur","ExaPum","SolAng","MurSim","NeaMon","VigVex","AsyDal","AdeInd","StrSes","CyaFas","CyaTub","ComBen")

#Using updated hex codes by taking average of the floral colour, rather than a single pixel
col_low <- c("IsoLop"="#d8d3d4","HabHey"="#cbccce","ParCoe"="#bfbebe","PinCon"="#bebdb5","EriSed"="#d0ccbe","PolChi"="#dedcae","SmiBig"="#fac926","SmiHir"="#e6b302","LinMys"="#dcc103","ImpDal"="#d9c636","SenBom"="#cdc131","MurLan"="#c19968","MurBro"="#db8051","SopDel"="#b36392","RotFlo"="#b64d8a","DesRac"="#c145a9","ImpTom"="#ef4ada","JusDif"="#b478ba","ImpBal"="#b36ebb","ImpLaw"="#9a4f95","PogDec"="#6a427a","UtrPur"="#583796","ExaPum"="#613e9d","SolAng"="#613e9d","MurSim"="#8f82b8","NeaMon"="#c699e7","VigVex"="#a57eb3","AsyDal"="#a175b3","AdeInd"="#a174bf","StrSes"="#8b6dc9","CyaFas"="#8a61f2","CyaTub"="#6253d2","ComBen"="#2b428e")

seq.high <- c("Bee","Beetle","Fly","Wasp","Ant","Butterfly","Moth")

col_high <-c("Bee"="#800000","Beetle"="#F08080","Fly"="#DC143C","Wasp"="#20B2AA","Ant"="#008080","Butterfly"="#FF7F50","Moth"="#98FB98")

#creating a list of two with two names vectors 
sequence <- list(seq.higher=seq.high, seq.lower=seq.low)
web.ordered <- sortweb(data_final, sort.order="seq", sequence=sequence)

plotweb(web.ordered, method="normal", text.rot=90, labsize=2.0, low.spacing=0.04, high.spacing=0.213, col.low= col_low, col.high = col_high, bor.col.low = col_low, bor.col.high = col_high, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")

#To save image
#png(filename = "Kaas_pollination_network_2018_&_2019.png", width = 16, height = 8.5, units = "in", bg = "white", res = 300)
#plotweb(web.ordered, method="normal", text.rot=90, labsize=2.0, low.spacing=0.04, high.spacing=0.213, col.low= col_low, col.high = col_high, bor.col.low = col_low, bor.col.high = col_high, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")
#dev.off()

```

5. Plotting the interactive network

Function frame2webs: To convert a table of observations (typically compiled in a spreadsheet program) into a network matrix for further use in bipartite.

```{r}
data.network <- frame2webs(sub_data_mean2, varnames = c("Flo_sp", "Pollinator_type", "WebID", "mean"))

#this will give only html output (interactive)
library(knitr)
bipartite_D3(data.network, PrimaryLab = 'Plants', SecondaryLab = 'Pollinators', PercentageDecimals = 3, filename = 'Overall_network_combined_2018_&_2019') 

```

6. Calculate indices: Overall flowering season for both the years (2018 & 2019)

```{r}

#To calculate the indices at network level
b <- networklevel(data.network [[1]], index="ALLBUTDD", level="both", weighted=TRUE, ISAmethod="Bluethgen", SAmethod = "Bluethgen", extinctmethod = "r", nrep = 100, CCfun=median, dist="horn", normalise=TRUE, empty.web=TRUE, logbase="e", intereven="prod", H2_integer=TRUE, fcweighted=TRUE, fcdist="euclidean", legacy=FALSE)

write.csv(b, file = "Cumulative_networklevel_indices_kaas_2018_&_2019.csv")

#To calculate the indices at species level: Plants
c <- specieslevel(data.network [[1]], index="ALLBUTD", level="lower", logbase=exp(1), low.abun=NULL, high.abun=NULL, PDI.normalise=TRUE, PSI.beta=c(1,0), nested.method="NODF", nested.normalised=TRUE, nested.weighted=TRUE, empty.web=TRUE)

write.csv(c, file = "Cumulative_Plant_specieslevel_indices_kaas_2018_&_2019.csv")

#To calculate the indices at species level: Pollinators
d <- specieslevel(data.network [[1]], index="ALLBUTD", level="higher", logbase=exp(1), low.abun=NULL, high.abun=NULL, PDI.normalise=TRUE, PSI.beta=c(1,0), nested.method="NODF", nested.normalised=TRUE, nested.weighted=TRUE, empty.web=TRUE)

write.csv(d, file = "Cumulative_Pollinator_specieslevel_indices_kaas_2018_&_2019.csv")
```

**Plotting season-wise network: 2018 & 2019 combined**

That is:
1. Pre-peak 
2. Peak 
3. Post-peak 

For this, we need to take mean of visitation rates according to census per species and pollinator type pair

1. Data processing

```{r}
#taking mean
library(plyr)
season_data_mean <- ddply(data_network, .(Flo_sp, Pollinator_type, Season), summarize, mean = mean(visitation_rate_per_flower_per_hour, Season = any(Season),  na.rm = TRUE))
#here month column can be used as WEBID

#To find the rows in which pollinator type is NA. With '!' the places with NA will be marked as FALSE and not considered in data-set.
x <- !is.na(season_data_mean$Pollinator_type) 
sub_season_data_mean <- season_data_mean[x,]

#Added the column with WebID as KAAS for 194 rows as bipartite function requires WebID
WebID = c(rep("KAAS", 194))
sub_season_data_mean2 = cbind(sub_season_data_mean, WebID)

```

2. Forming a network matrix

```{r}
data.network.season <- frame2webs(sub_season_data_mean2, varnames = c("Flo_sp", "Pollinator_type", "Season", "mean") )
```

3. Plotting an interactive network

```{r}
#this will give only html output (interactive)

bipartite_D3(data.network.season, PrimaryLab = 'Plants', SecondaryLab = 'Pollinators', PercentageDecimals = 1, filename = 'network_season_wise_2018_&_2019')
```
4. Plotting the non-interactive network

```{r}

#Sort the data according to seasons, i.e., extract the data season-wise

Pre_peak_network_data<- subset(sub_season_data_mean2, sub_season_data_mean2$Season == "Pre-peak")
Peak_network_data<- subset(sub_season_data_mean2, sub_season_data_mean2$Season == "Peak")
Post_peak_network_data<- subset(sub_season_data_mean2, sub_season_data_mean2$Season == "Post-peak")

```

```{r}

#**For Pre-peak**

Pre_peak_dcast<-dcast(Pre_peak_network_data, Flo_sp ~ Pollinator_type, value.var = "mean")  
#Replacing all NA with zeros
Pre_peak_dcast[is.na(Pre_peak_dcast)]=0
#Removing the 6th column as the column name is 'NA'
Pre_peak_dcast = Pre_peak_dcast[,-6]
row.names(Pre_peak_dcast) <- Pre_peak_dcast$Flo_sp
#Remove the first column
Pre_peak_dcast = Pre_peak_dcast[,-1]

#Round of the values to 1 decimal point
Pre_peak_dcast2 = round(Pre_peak_dcast, 1)

#removing the species that have all 0, that is, no visitation by any pollinator type
#subsetting the data as 'data_final'

Pre_peak_final <- Pre_peak_dcast2[rowSums(Pre_peak_dcast2[])>0,]

#To plot species as per your desired sequence, add them in a sequence inside a particular vector and mention it as 'seq.high' and 'seq.low' in plotweb function.

seq.low_pre <- c("HabHey","ParCoe","PinCon","EriSed","ImpDal","SenBom","ImpTom","JusDif","ImpBal","ImpLaw","PogDec","ExaPum","MurSim","NeaMon","CyaTub")

col_low_pre <- c("HabHey"="#cbccce","ParCoe"="#bfbebe","PinCon"="#bebdb5","EriSed"="#d0ccbe","ImpDal"="#d9c636","SenBom"="#cdc131","ImpTom"="#ef4ada","JusDif"="#b478ba","ImpBal"="#b36ebb","ImpLaw"="#9a4f95","PogDec"="#6a427a","ExaPum"="#613e9d","MurSim"="#8f82b8","NeaMon"="#c699e7","CyaTub"="#6253d2")

seq.high_pre <- c("Fly","Bee","Beetle","Wasp","Ant")

col_high_pre <-c("Fly"="#DC143C","Bee"="#800000","Beetle"="#F08080","Wasp"="#20B2AA","Ant"="#008080")

#creating a list of two with two names vectors
sequence_pre <- list(seq.higher=seq.high_pre, seq.lower=seq.low_pre)
web.ordered_pre <- sortweb(Pre_peak_final, sort.order="seq", sequence=sequence_pre)

plotweb(web.ordered_pre, method="normal", text.rot=90, labsize=2.0, low.spacing=0.04, high.spacing=0.135, col.low= col_low_pre, col.high = col_high_pre, bor.col.low = col_low_pre, bor.col.high = col_high_pre, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")

#Copy-paste the code for plotweb in new 'R Script' to export the image as png with the desired aspect ratio (1600 width x 850 height)
#png(filename = "Pre-peak_Kaas_pollination_network_2018_&_2019.png", width = 16, height = 8.5, units = "in",bg = "white", res = 300)
#plotweb(web.ordered_pre, method="normal", text.rot=90, labsize=2.0, low.spacing=0.04, high.spacing=0.135, col.low= col_low_pre, col.high = col_high_pre, bor.col.low = col_low_pre, bor.col.high = col_high_pre, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")
#dev.off()

```

**For Peak flowering season**

```{r}

Peak_dcast<-dcast(Peak_network_data, Flo_sp ~ Pollinator_type, value.var = "mean")  
#Replacing all NA with zeros
Peak_dcast[is.na(Peak_dcast)]=0
#Removing the 8th column as the column name is 'NA'
Peak_dcast = Peak_dcast[,-8]
row.names(Peak_dcast) <- Peak_dcast$Flo_sp
#Remove the first column
Peak_dcast = Peak_dcast[,-1]

#Round of the values to 1 decimal point
Peak_dcast2 = round(Peak_dcast, 1)

#removing the species that have all 0, that is, no visitation by any pollinator type
#subsetting the data as 'data_final'

Peak_final <- Peak_dcast2[rowSums(Peak_dcast2[])>0,]

#To plot species as per your desired sequence, add them in a sequence inside a particular vector and mention it as 'seq.high' and 'seq.low' in plotweb function.

seq.low_peak <- c("IsoLop","ParCoe","PinCon","EriSed","SmiBig","SmiHir","SenBom","MurLan","MurBro","SopDel","RotFlo","ImpTom","JusDif","ImpBal","PogDec","UtrPur","SolAng","MurSim","NeaMon","AsyDal","AdeInd","StrSes","CyaFas","CyaTub","ComBen")

col_low_peak <- c("IsoLop"="#d8d3d4","ParCoe"="#bfbebe","PinCon"="#bebdb5","EriSed"="#d0ccbe","SmiBig"="#fac926","SmiHir"="#e6b302","SenBom"="#cdc131","MurLan"="#c19968","MurBro"="#db8051","SopDel"="#b36392","RotFlo"="#b64d8a","ImpTom"="#ef4ada","JusDif"="#b478ba","ImpBal"="#b36ebb","PogDec"="#6a427a","UtrPur"="#583796","SolAng"="#613e9d","MurSim"="#8f82b8","NeaMon"="#c699e7","AsyDal"="#a175b3","AdeInd"="#a174bf","StrSes"="#8b6dc9","CyaFas"="#8a61f2","CyaTub"="#6253d2","ComBen"="#2b428e")

seq.high_peak <- c("Bee","Fly","Beetle","Butterfly","Wasp","Moth")

col_high_peak <-c("Bee"="#800000","Fly"="#DC143C","Beetle"="#F08080","Butterfly"="#FF7F50","Wasp"="#20B2AA","Moth"="#98FB98")

#creating a list of two with two names vectors
sequence_peak <- list(seq.higher=seq.high_peak, seq.lower=seq.low_peak)
web.ordered_peak <- sortweb(Peak_final, sort.order="seq", sequence=sequence_peak)

plotweb(web.ordered_peak, method="normal", text.rot=90, labsize=2.0, low.spacing=0.04, high.spacing=0.193, col.low= col_low_peak, col.high = col_high_peak, bor.col.low = col_low_peak, bor.col.high = col_high_peak, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")

#Copy-paste the code for plotweb in new 'R Script' to export the image as png with the desired aspect ratio 
#(1600 width x 850 height)
#png(filename = "Peak_Kaas_pollination_network_2018_&_2019.png", width = 16, height = 8.5, units = "in",bg = "white", res = 300)
#plotweb(web.ordered_peak, method="normal", text.rot=90, labsize=2.0, low.spacing=0.04, high.spacing=0.193, col.low= col_low_peak, col.high = col_high_peak, bor.col.low = col_low_peak, bor.col.high = col_high_peak, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")
#dev.off()

```

**For Post-peak flowering season**

```{r}

Post_peak_dcast<-dcast(Post_peak_network_data, Flo_sp ~ Pollinator_type, value.var = "mean")  
#Replacing all NA with zeros
Post_peak_dcast[is.na(Post_peak_dcast)]=0
#Removing the 8th column as the column name is 'NA'
Post_peak_dcast = Post_peak_dcast[,-8]
row.names(Post_peak_dcast) <- Post_peak_dcast$Flo_sp
#Remove the first column
Post_peak_dcast = Post_peak_dcast[,-1]

#Round of the values to 1 decimal point
Post_peak_dcast2 = round(Post_peak_dcast, 1)

#removing the species that have all 0, that is, no visitation by any pollinator type
#subsetting the data as 'data_final'

Post_peak_final <- Post_peak_dcast2[rowSums(Post_peak_dcast2[])>0,]

#To plot species as per your desired sequence, add them in a sequence inside a particular vector and mention it as 'seq.high' and 'seq.low' in plotweb function.

seq.low_post <- c("IsoLop","ParCoe","PolChi","SmiBig","SmiHir","LinMys","SenBom","MurLan", "MurBro","SopDel","RotFlo","DesRac","PogDec","SolAng","NeaMon","VigVex","AdeInd","StrSes","CyaTub","ComBen")

col_low_post <- c("IsoLop"="#d8d3d4","ParCoe"="#bfbebe","PolChi"="#dedcae","SmiBig"="#fac926","SmiHir"="#e6b302","LinMys"="#dcc103","SenBom"="#cdc131","MurLan"="#c19968","MurBro"="#db8051","SopDel"="#b36392","RotFlo"="#b64d8a","DesRac"="#c145a9","PogDec"="#6a427a","SolAng"="#613e9d","NeaMon"="#c699e7","VigVex"="#a57eb3","AdeInd"="#a174bf","StrSes"="#8b6dc9","CyaTub"="#6253d2","ComBen"="#2b428e")

seq.high_post <- c("Bee","Beetle","Fly","Wasp","Butterfly","Moth","Ant")

col_high_post <-c("Bee"="#800000","Beetle"="#F08080","Fly"="#DC143C","Wasp"="#20B2AA","Butterfly"="#FF7F50","Moth"="#98FB98","Ant"="#008080")

#creating a list of two with two names vectors
sequence_post <- list(seq.higher=seq.high_post, seq.lower=seq.low_post)
web.ordered_post <- sortweb(Post_peak_final, sort.order="seq", sequence=sequence_post)

plotweb(web.ordered_post, method="normal", text.rot=90, labsize=2.0, low.spacing=0.04, high.spacing=0.127, col.low= col_low_post, col.high = col_high_post, bor.col.low = col_low_post, bor.col.high = col_high_post, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")

#Copy-paste the code for plotweb in new 'R Script' to export the image as png with the desired aspect ratio 
#(1600 width x 850 height)
#png(filename = "Post-peak_Kaas_pollination_network_2018_&_2019.png", width = 16, height = 8.5, units = "in",bg = "white", res = 300)
#plotweb(web.ordered_post, method="normal", text.rot=90, labsize=2.0, low.spacing=0.04, high.spacing=0.127, col.low= col_low_post, col.high = col_high_post, bor.col.low = col_low_post, bor.col.high = col_high_post, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")
#dev.off()

```

5. Calculating indices: Season-wise across both years (2018 & 2019)

5.1 : Pre-peak season
5.2 : Peak season
5.3 : Post-peak season



5.1 : Pre-peak season

```{r}

#To calculate the indices, we need the data in network matrix format.
#'frame2webs' coverts table of observations into network matrix
#I am using the sub-setted data after taking mean

pre.data.network <- frame2webs(Pre_peak_network_data, varnames = c("Flo_sp", "Pollinator_type", "WebID", "mean"))

#To calculate the indices at network level
b_pre <- networklevel(pre.data.network [[1]], index="ALLBUTDD", level="both", weighted=TRUE, ISAmethod="Bluethgen", SAmethod = "Bluethgen", extinctmethod = "r", nrep = 100, CCfun=median, dist="horn", normalise=TRUE, empty.web=TRUE, logbase="e", intereven="prod", H2_integer=TRUE, fcweighted=TRUE, fcdist="euclidean", legacy=FALSE)

write.csv(b_pre, file = "PRE-PEAK_networklevel_indices_kaas_2018_&_2019.csv")

#To calculate the indices at species level: Plants
c_pre <- specieslevel(pre.data.network [[1]], index="ALLBUTD", level="lower", logbase=exp(1), low.abun=NULL, high.abun=NULL, PDI.normalise=TRUE, PSI.beta=c(1,0), nested.method="NODF", nested.normalised=TRUE, nested.weighted=TRUE, empty.web=TRUE)

write.csv(c_pre, file = "PRE-PEAK_plant_specieslevel_indices_kaas_2018_&_2019.csv")

#To calculate the indices at species level: Pollinators
d_pre <- specieslevel(pre.data.network [[1]], index="ALLBUTD", level="higher", logbase=exp(1), low.abun=NULL, high.abun=NULL, PDI.normalise=TRUE, PSI.beta=c(1,0), nested.method="NODF", nested.normalised=TRUE, nested.weighted=TRUE, empty.web=TRUE)

write.csv(d_pre, file = "PRE-PEAK_pollinator_specieslevel_indices_kaas_2018_&_2019.csv")
```

5.2 : Peak season

```{r}

peak.data.network <- frame2webs(Peak_network_data, varnames = c("Flo_sp", "Pollinator_type", "WebID", "mean"))

#To calculate the indices at network level
b_peak <- networklevel(peak.data.network[[1]], index="ALLBUTDD", level="both", weighted=TRUE, ISAmethod="Bluethgen", SAmethod = "Bluethgen", extinctmethod = "r", nrep = 100, CCfun=median, dist="horn", normalise=TRUE, empty.web=TRUE, logbase="e", intereven="prod", H2_integer=TRUE, fcweighted=TRUE, fcdist="euclidean", legacy=FALSE)

write.csv(b_peak, file = "PEAK_networklevel_indices_kaas_2018_&_2019.csv")

#To calculate the indices at species level: Plants
c_peak <- specieslevel(peak.data.network [[1]], index="ALLBUTD", level="lower", logbase=exp(1), low.abun=NULL, high.abun=NULL, PDI.normalise=TRUE, PSI.beta=c(1,0), nested.method="NODF", nested.normalised=TRUE, nested.weighted=TRUE, empty.web=TRUE)

write.csv(c_peak, file = "PEAK_plant_specieslevel_indices_kaas_2018_&_2019.csv")

#To calculate the indices at species level: Pollinators
d_peak <- specieslevel(peak.data.network [[1]], index="ALLBUTD", level="higher", logbase=exp(1), low.abun=NULL, high.abun=NULL, PDI.normalise=TRUE, PSI.beta=c(1,0), nested.method="NODF", nested.normalised=TRUE, nested.weighted=TRUE, empty.web=TRUE)

write.csv(d_peak, file = "PEAK_pollinator_specieslevel_indices_kaas_2018_&_2019.csv")
```

5.3 : Post-peak season

```{r}

post.data.network <- frame2webs(Post_peak_network_data, varnames = c("Flo_sp", "Pollinator_type", "WebID", "mean"))

#To calculate the indices at network level
b_post <- networklevel(post.data.network [[1]], index="ALLBUTDD", level="both", weighted=TRUE, ISAmethod="Bluethgen", SAmethod = "Bluethgen", extinctmethod = "r", nrep = 100, CCfun=median, dist="horn", normalise=TRUE, empty.web=TRUE, logbase="e", intereven="prod", H2_integer=TRUE, fcweighted=TRUE, fcdist="euclidean", legacy=FALSE)

write.csv(b_post, file = "POST-PEAK_networklevel_indices_kaas_2018_&_2019.csv")

#To calculate the indices at species level: Plants
c_post <- specieslevel(post.data.network [[1]], index="ALLBUTD", level="lower", logbase=exp(1), low.abun=NULL, high.abun=NULL, PDI.normalise=TRUE, PSI.beta=c(1,0), nested.method="NODF", nested.normalised=TRUE, nested.weighted=TRUE, empty.web=TRUE)

write.csv(c_post, file = "POST-PEAK_plant_specieslevel_indices_kaas_2018_&_2019.csv")

#To calculate the indices at species level: Pollinators
d_post <- specieslevel(post.data.network [[1]], index="ALLBUTD", level="higher", logbase=exp(1), low.abun=NULL, high.abun=NULL, PDI.normalise=TRUE, PSI.beta=c(1,0), nested.method="NODF", nested.normalised=TRUE, nested.weighted=TRUE, empty.web=TRUE)

write.csv(d_post, file = "POST-PEAK_pollinator_specieslevel_indices_kaas_2018_&_2019.csv")
```

**Plotting MF-nMF network: 2018 & 2019 combined**
1. MF
2. nMF

For this, we need to take mean of visitation rates according to MF/nMF per species and pollinator type pair

1. Data processing

```{r}
#taking mean
library(plyr)
abundance_data_mean <- ddply(data_network, .(Flo_sp, Pollinator_type, MF_nMF), summarize, mean = mean(visitation_rate_per_flower_per_hour, MF_nMF = any(MF_nMF),  na.rm = TRUE))
#here MF_nMF column can be used as WEBID

#To find the rows in which pollinator type is NA. With '!' the places with NA will be marked as FALSE and not considered in data-set.
x <- !is.na(abundance_data_mean$Pollinator_type) 
sub_abundance_data_mean <- abundance_data_mean[x,]

#Added the column with WebID as KAAS for 130 rows as bipartite function requires WebID
WebID = c(rep("KAAS", 130))
sub_abundance_data_mean2 = cbind(sub_abundance_data_mean, WebID)

```

2. Forming a network matrix

```{r}
data.network.abundance <- frame2webs(sub_abundance_data_mean2, varnames = c("Flo_sp", "Pollinator_type", "MF_nMF", "mean") )
```

3. Plotting an interactive network

```{r}
#this will give only html output (interactive)

bipartite_D3(data.network.abundance, PrimaryLab = 'Plants', SecondaryLab = 'Pollinators', PercentageDecimals = 1, filename = 'network_abundance_wise_2018_&_2019')
```

4. Plotting the non-interactive network

```{r}

#Sort the data according to MF/nMF, i.e., extract the data abundance-wise

MF_data<- subset(sub_abundance_data_mean2, sub_abundance_data_mean$MF_nMF == "MF")
nMF_data<- subset(sub_abundance_data_mean2, sub_abundance_data_mean2$MF_nMF == "nMF")

```

```{r}

#**For MF**

MF_dcast<-dcast(MF_data, Flo_sp ~ Pollinator_type, value.var = "mean")  
#Replacing all NA with zeros
MF_dcast[is.na(MF_dcast)]=0
#Removing the 8th column as the column name is 'NA'
MF_dcast = MF_dcast[,-8]
row.names(MF_dcast) <- MF_dcast$Flo_sp
#Remove the first column
MF_dcast = MF_dcast[,-1]

#Round of the values to 1 decimal point
MF_dcast2 = round(MF_dcast, 1)

#removing the species that have all 0, that is, no visitation by any pollinator type
#subsetting the data as 'data_final'

MF_final <- MF_dcast2[rowSums(MF_dcast2[])>0,]

#To plot species as per your desired sequence, add them in a sequence inside a particular vector and mention it as 'seq.high' and 'seq.low' in plotweb function.

seq.low_MF <- c("EriSed","SenBom","LinMys","SmiHir","ImpTom","RotFlo","ImpLaw","UtrPur","CyaFas")
              
col_low_MF <- c("EriSed"="#d0ccbe","SenBom"="#cdc131","LinMys"="#dcc103","SmiHir"="#e6b302","ImpTom"="#ef4ada","RotFlo"="#b64d8a","ImpLaw"="#9a4f95","UtrPur"="#583796","CyaFas"="#8a61f2")
                 
seq.high_MF <- c("Bee","Fly","Beetle","Wasp","Ant","Butterfly","Moth")

col_high_MF <-c("Bee"="#800000","Fly"="#DC143C","Beetle"="#F08080","Wasp"="#20B2AA","Ant"="#008080","Butterfly"="#FF7F50","Moth"="#98FB98")

#creating a list of two with two names vectors
sequence_MF <- list(seq.higher=seq.high_MF, seq.lower=seq.low_MF)
web.ordered_MF <- sortweb(MF_final, sort.order="seq", sequence=sequence_MF)

plotweb(web.ordered_MF, method="normal", text.rot=90, labsize=2.0, low.spacing=0.05, high.spacing=0.064, col.low= col_low_MF, col.high = col_high_MF, bor.col.low = col_low_MF, bor.col.high = col_high_MF, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")

#Copy-paste the code for plotweb in new 'R Script' to export the image as png with the desired aspect ratio (1600 width x 850 height)
#png(filename = "MF_Kaas_pollination_network_2018_&_2019.png", width = 16, height = 8.5, units = "in",bg = "white", res = 300)
#plotweb(web.ordered_MF, method="normal", text.rot=90, labsize=2.0, low.spacing=0.05, high.spacing=0.064, col.low= col_low_MF, col.high = col_high_MF, bor.col.low = col_low_MF, bor.col.high = col_high_MF, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")
#dev.off()

```

```{r}

#**For nMF**

nMF_dcast<-dcast(nMF_data, Flo_sp ~ Pollinator_type, value.var = "mean")  
#Replacing all NA with zeros
nMF_dcast[is.na(nMF_dcast)]=0
#Removing the 8th column as the column name is 'NA'
nMF_dcast = nMF_dcast[,-8]
row.names(nMF_dcast) <- nMF_dcast$Flo_sp
#Remove the first column
nMF_dcast = nMF_dcast[,-1]

#Round of the values to 1 decimal point
nMF_dcast2 = round(nMF_dcast, 1)

#removing the species that have all 0, that is, no visitation by any pollinator type
#subsetting the data as 'data_final'

nMF_final <- nMF_dcast2[rowSums(nMF_dcast2[])>0,]

#To plot species as per your desired sequence, add them in a sequence inside a particular vector and mention it as 'seq.high' and 'seq.low' in plotweb function.

seq.low_nMF <- c("IsoLop","HabHey","ParCoe","PinCon","PolChi","SmiBig","ImpDal","MurLan","MurBro","SopDel","DesRac","JusDif","ImpBal","PogDec","ExaPum","SolAng","MurSim","NeaMon","VigVex","AsyDal","AdeInd","StrSes","CyaTub","ComBen") 
              
col_low_nMF <- c("IsoLop"="#d8d3d4","HabHey"="#cbccce","ParCoe"="#bfbebe","PinCon"="#bebdb5","PolChi"="#dedcae","SmiBig"="#fac926","ImpDal"="#d9c636","MurLan"="#c19968","MurBro"="#db8051","SopDel"="#b36392","DesRac"="#c145a9","JusDif"="#b478ba","ImpBal"="#b36ebb","PogDec"="#6a427a","ExaPum"="#613e9d","SolAng"="#613e9d","MurSim"="#8f82b8","NeaMon"="#c699e7","VigVex"="#a57eb3","AsyDal"="#a175b3","AdeInd"="#a174bf","StrSes"="#8b6dc9","CyaTub"="#6253d2","ComBen"="#2b428e")
                 
seq.high_nMF <- c("Bee","Beetle","Fly","Wasp","Ant","Butterfly","Moth")

col_high_nMF <-c("Bee"="#800000","Beetle"="#F08080","Fly"="#DC143C","Wasp"="#20B2AA","Ant"="#008080","Butterfly"="#FF7F50","Moth"="#98FB98")

#creating a list of two with two names vectors
sequence_nMF <- list(seq.higher=seq.high_nMF, seq.lower=seq.low_nMF)
web.ordered_nMF <- sortweb(nMF_final, sort.order="seq", sequence=sequence_nMF)

plotweb(web.ordered_nMF, method="normal", text.rot=90, labsize=2.0, low.spacing=0.1, high.spacing=0.375, col.low= col_low_nMF, col.high = col_high_nMF, bor.col.low = col_low_nMF, bor.col.high = col_high_nMF, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")

#Copy-paste the code for plotweb in new 'R Script' to export the image as png with the desired aspect ratio (1600 width x 850 height)
#png(filename = "nMF_Kaas_pollination_network_2018_&_2019.png", width = 16, height = 8.5, units = "in",bg = "white", res = 300)
#plotweb(web.ordered_nMF, method="normal", text.rot=90, labsize=2.0, low.spacing=0.1, high.spacing=0.375, col.low= col_low_nMF, col.high = col_high_nMF, bor.col.low = col_low_nMF, bor.col.high = col_high_nMF, text.high.col = "black", text.low.col = "black", col.interaction = "gray", bor.col.interaction = "gray")
#dev.off()

```



**Nested contribution according species: Cumulative network**

```{r}
nestcont = nestedcontribution(data_final, nsimul = 100)

#To save the output as csv file as it provides the data in list format. 
#Use the $ sign to separately save for pollinators and plants.

write.csv(nestcont$`higher level`, file = "CUMULATIVE_Nested_contri_pollinator_Kaas_2018_&_2019.csv")

write.csv(nestcont$`lower level`, file = "CUMULATIVE_Nested_contri_plant_Kaas_2018_&_2019.csv")
```

**Nested contribution according species: season-wise network**

1. Pre-peak network:
```{r}

nestcont_pre = nestedcontribution(Pre_peak_final, nsimul = 100)

write.csv(nestcont_pre$`higher level`, file = "PRE-PEAK_Nested_contri_pollinator_Kaas_2018_&_2019.csv")

write.csv(nestcont_pre$`lower level`, file = "PRE-PEAK_Nested_contri_plant_Kaas_2018_&_2019.csv")

```

2. Peak network:
```{r}

nestcont_peak = nestedcontribution(Peak_final, nsimul = 100)

write.csv(nestcont_peak$`higher level`, file = "PEAK_Nested_contri_pollinator_Kaas_2018_&_2019.csv")

write.csv(nestcont_peak$`lower level`, file = "PEAK_Nested_contri_plant_Kaas_2018_&_2019.csv")
```

3. Post-peak network:
```{r}
nestcont_post = nestedcontribution(Post_peak_final, nsimul = 100)

write.csv(nestcont_post$`higher level`, file = "POST-PEAK_Nested_contri_pollinator_Kaas_2018_&_2019.csv")

write.csv(nestcont_post$`lower level`, file = "POST-PEAK_Nested_contri_plant_Kaas_2018_&_2019.csv")

```




