---
title: "Synchrony calculations for 2018 and 2019"
output: html_notebook
---

Performing analysis for year 2018

read the file
```{r}
mydata_2018 = read.csv("Kaas_Phenology_2018.csv")
```


Calculating both SIabd and SItemp
```{r}
# Extract species codes and phenological data
species_codes <- mydata_2018$Species_code
phenological_data <- mydata_2018[, 6:11]

# Define a function to calculate SItemp
calculate_SItemp <- function(F1, F2, Fo) {
  SItemp <- Fo / ((F1 + F2) - Fo)
  return(SItemp)
}

# Define a function to calculate SIabd
calculate_SIabd <- function(species1, species2) {
  # Calculate proportions for each census reading (abundance of less abundant species divided by abundance of more abundant species)
  proportions <- pmin(species1, species2) / pmax(species1, species2)
  # Calculate the average proportion where both species were recorded (n)
  SIabd <- mean(proportions[!is.na(proportions)], na.rm = TRUE)
  return(SIabd)
}

# Initialize a data frame to store results for each species pair
results_df <- data.frame(species1 = character(), species2 = character(),
                         F1 = numeric(), F2 = numeric(), Fo = numeric(),
                         SItemp = numeric(), SIabd = numeric(),
                         stringsAsFactors = FALSE)

# Loop through all species pairs and calculate SItemp and SIabd
num_species <- nrow(phenological_data)

for (i in 1:(num_species - 1)) {
  for (j in (i + 1):num_species) {
    species1 <- phenological_data[i, ]
    species2 <- phenological_data[j, ]
    
    # Calculate total flowering duration (number of census days in flowering)
    F1 <- sum(!is.na(species1) & species1 != 0)
    F2 <- sum(!is.na(species2) & species2 != 0)
    
    # Calculate temporal overlap in flowering (Fo)
    Fo <- sum(!is.na(species1) & !is.na(species2) & species1 != 0 & species2 != 0)
    
    # Calculate SItemp
    SItemp <- calculate_SItemp(F1, F2, Fo)
    
    # Calculate SIabd only if SItemp > 0
    if (SItemp > 0) {
      SIabd <- calculate_SIabd(species1, species2)
    } else {
      SIabd <- NA
    }
    
    # Store the results in the data frame
    results_df <- rbind(results_df, data.frame(species1 = species_codes[i], species2 = species_codes[j],
                                               F1 = F1, F2 = F2, Fo = Fo, SItemp = SItemp, SIabd = SIabd))
  }
}

# Print the final data frame in the desired format
print(results_df)

#save the final data frame as SI_2018
SI_2018 <- results_df
```

Remove all rows with EriSed
```{r}
library(dplyr)
SI_2018 <- SI_2018 %>%
  filter(!grepl("EriSed", species1) & !grepl("EriSed", species2))
```


Calculating mean SI

```{r}

Mean_SItemp2018= mean(SI_2018$SItemp)
SD_SItemp2018 = sd(SI_2018$SItemp) 
sem_SItemp2018= SD_SItemp2018/sqrt(length(SI_2018$SItemp)/2)

Mean_SIabd2018 = mean(SI_2018$SIabd, na.rm = T)
SD_SIabd2018 = sd(SI_2018$SIabd, na.rm = T) 
sem_SIabd2018 = SD_SIabd2018/sqrt(sum(!is.na(SI_2018$SIabd))/2)
```

Save output as csv
```{r}
write.csv(SI_2018, file = "Synchrony_Index_2018.csv", na = "NA")
```


Performing analysis for year 2019

read the file
```{r}
mydata_2019 = read.csv("Kaas_Phenology_2019.csv")
```


Calculating both SIabd and SItemp
```{r}
# Extract species codes and phenological data
species_codes <- mydata_2019$Species_code
phenological_data <- mydata_2019[, 6:13]

# Define a function to calculate SItemp
calculate_SItemp <- function(F1, F2, Fo) {
  SItemp <- Fo / ((F1 + F2) - Fo)
  return(SItemp)
}

# Define a function to calculate SIabd
calculate_SIabd <- function(species1, species2) {
  # Calculate proportions for each census reading (abundance of less abundant species divided by abundance of more abundant species)
  proportions <- pmin(species1, species2) / pmax(species1, species2)
  # Calculate the average proportion where both species were recorded (n)
  SIabd <- mean(proportions[!is.na(proportions)], na.rm = TRUE)
  return(SIabd)
}

# Initialize a data frame to store results for each species pair
results_df <- data.frame(species1 = character(), species2 = character(),
                         F1 = numeric(), F2 = numeric(), Fo = numeric(),
                         SItemp = numeric(), SIabd = numeric(),
                         stringsAsFactors = FALSE)

# Loop through all species pairs and calculate SItemp and SIabd
num_species <- nrow(phenological_data)

for (i in 1:(num_species - 1)) {
  for (j in (i + 1):num_species) {
    species1 <- phenological_data[i, ]
    species2 <- phenological_data[j, ]
    
    # Calculate total flowering duration (number of days in flowering)
    F1 <- sum(!is.na(species1) & species1 != 0)
    F2 <- sum(!is.na(species2) & species2 != 0)
    
    # Calculate temporal overlap in flowering (Fo)
    Fo <- sum(!is.na(species1) & !is.na(species2) & species1 != 0 & species2 != 0)
    
    # Calculate SItemp
    SItemp <- calculate_SItemp(F1, F2, Fo)
    
    # Calculate SIabd only if SItemp > 0
    if (SItemp > 0) {
      SIabd <- calculate_SIabd(species1, species2)
    } else {
      SIabd <- NA
    }
    
    # Store the results in the data frame
    results_df <- rbind(results_df, data.frame(species1 = species_codes[i], species2 = species_codes[j],
                                               F1 = F1, F2 = F2, Fo = Fo, SItemp = SItemp, SIabd = SIabd))
  }
}

# Print the final data frame in the desired format
print(results_df)

#save the final data frame as SI_2019
SI_2019 <- results_df
```

Remove all rows with EriSed
```{r}
library(dplyr)
SI_2019 <- SI_2019 %>%
  filter(!grepl("EriSed", species1) & !grepl("EriSed", species2))
```




Calculating mean SI

```{r}

Mean_SItemp2019= mean(SI_2019$SItemp)
SD_SItemp2019 = sd(SI_2019$SItemp) 
sem_SItemp2019= SD_SItemp2019/sqrt(length(SI_2019$SItemp)/2)

Mean_SIabd2019 = mean(SI_2019$SIabd, na.rm = T)
SD_SIabd2019 = sd(SI_2019$SIabd, na.rm = T) 
sem_SIabd2019 = SD_SIabd2019/sqrt(sum(!is.na(SI_2019$SIabd))/2)
```


Save output as csv
```{r}
write.csv(SI_2019, file = "Synchrony_Index_2019.csv", na = "NA")
```


Performing analysis for year 2020

read the file
```{r}
mydata_2020 = read.csv("Kaas_Phenology_2020.csv")
```


Calculating both SIabd and SItemp
```{r}
# Extract species codes and phenological data
species_codes <- mydata_2020$Species_code
phenological_data <- mydata_2020[, 6:23]

# Define a function to calculate SItemp
calculate_SItemp <- function(F1, F2, Fo) {
  SItemp <- Fo / ((F1 + F2) - Fo)
  return(SItemp)
}

# Define a function to calculate SIabd
calculate_SIabd <- function(species1, species2) {
  # Calculate proportions for each census reading (abundance of less abundant species divided by abundance of more abundant species)
  proportions <- pmin(species1, species2) / pmax(species1, species2)
  # Calculate the average proportion where both species were recorded (n)
  SIabd <- mean(proportions[!is.na(proportions)], na.rm = TRUE)
  return(SIabd)
}

# Initialize a data frame to store results for each species pair
results_df <- data.frame(species1 = character(), species2 = character(),
                         F1 = numeric(), F2 = numeric(), Fo = numeric(),
                         SItemp = numeric(), SIabd = numeric(),
                         stringsAsFactors = FALSE)

# Loop through all species pairs and calculate SItemp and SIabd
num_species <- nrow(phenological_data)

for (i in 1:(num_species - 1)) {
  for (j in (i + 1):num_species) {
    species1 <- phenological_data[i, ]
    species2 <- phenological_data[j, ]
    
    # Calculate total flowering duration (number of census days in flowering)
    F1 <- sum(!is.na(species1) & species1 != 0)
    F2 <- sum(!is.na(species2) & species2 != 0)
    
    # Calculate temporal overlap in flowering (Fo)
    Fo <- sum(!is.na(species1) & !is.na(species2) & species1 != 0 & species2 != 0)
    
    # Calculate SItemp
    SItemp <- calculate_SItemp(F1, F2, Fo)
    
    # Calculate SIabd only if SItemp > 0
    if (SItemp > 0) {
      SIabd <- calculate_SIabd(species1, species2)
    } else {
      SIabd <- NA
    }
    
    # Store the results in the data frame
    results_df <- rbind(results_df, data.frame(species1 = species_codes[i], species2 = species_codes[j],
                                               F1 = F1, F2 = F2, Fo = Fo, SItemp = SItemp, SIabd = SIabd))
  }
}

# Print the final data frame in the desired format
print(results_df)

#save the final data frame as SI_2018
SI_2020 <- results_df
```


Write the species colour and MF-nMF status for respective species in data SI_2020
```{r}
# Create a new column in mydata with the corresponding flower color
library(dplyr)
SI_2020 <- SI_2020 %>%
  mutate(col_grp_species1 = mydata_2020$Colour_groups[match(species1, mydata_2020$Species_code)])

SI_2020 <- SI_2020 %>%
  mutate(col_grp_species2 = mydata_2020$Colour_groups[match(species2, mydata_2020$Species_code)])

SI_2020 <- SI_2020 %>%
  mutate(MF_nMF_Sp1 = mydata_2020$MF_nMF[match(species1, mydata_2020$Species_code)])

SI_2020 <- SI_2020 %>%
  mutate(MF_nMF_Sp2 = mydata_2020$MF_nMF[match(species2, mydata_2020$Species_code)])

```


Remove all rows with EriSed
```{r}
library(dplyr)
SI_2020 <- SI_2020 %>%
  filter(!grepl("EriSed", species1) & !grepl("EriSed", species2))
```

Save output as csv
```{r}
write.csv(SI_2020, file = "Synchrony_Index_2020.csv", na = "NA")
```


Calculating mean SI

```{r}
Mean_SItemp2020= mean(SI_2020$SItemp)
SD_SItemp2020 = sd(SI_2020$SItemp) 
sem_SItemp2020= SD_SItemp2020/sqrt(length(SI_2020$SItemp)/2)

Mean_SIabd2020 = mean(SI_2020$SIabd, na.rm = T)
SD_SIabd2020 = sd(SI_2020$SIabd, na.rm = T) 
sem_SIabd2020 = SD_SIabd2020/sqrt(sum(!is.na(SI_2020$SIabd))/2)
```



Comparing SItemp and SIabd among colour groups.

```{r}
# first combinie values of two colour columns to create a unique colour combination
SI_2020$Col_grp_Sp12<-paste(SI_2020$col_grp_species1, SI_2020$col_grp_species2, sep="_")

#calculating mean and sem for the each colour comparison for SItemp
library(plyr)

aa = ddply(SI_2020, .(Col_grp_Sp12), summarise,
                                      Mean_SItemp = mean(SItemp),
                                      SD = sd(SItemp),
                                      sem = SD/ sqrt(length(SItemp)))
aa


#drop NA rows from SIabd column
library(tidyr)
SI_2020_abd = SI_2020 %>% drop_na(SIabd)

bb = ddply(SI_2020_abd, .(Col_grp_Sp12), summarise,
                                      Mean_SIabd = mean(SIabd, na.rm = T),
                                      SD = sd(SIabd, na.rm = T),
                                      sem = SD/ sqrt(length(SIabd)))
bb


aabb <- cbind(aa, bb)
write.csv(aabb, file = "mean_sem for colour group combinations_2020 data.csv")

```

performing test for SItemp
```{r}
kruskal.test(SItemp ~ Col_grp_Sp12, data = SI_2020)

library(dunn.test)
dunn.test(SI_2020$SItemp, SI_2020$Col_grp_Sp12)
```
Similarly running test for for SIabd



performing test for SIabd
```{r}
kruskal.test(SIabd ~ Col_grp_Sp12, data = SI_2020_abd)

library(dunn.test)
dunn.test(SI_2020_abd$SIabd, SI_2020_abd$Col_grp_Sp12)
```


Analysing synchrony among/within MF and nMF species

```{r}
# first combinie values of two colour columns to create a unique MF_nMF combination
SI_2020$MF_nMF_Sp12<-paste(SI_2020$MF_nMF_Sp1, SI_2020$MF_nMF_Sp2, sep="_")


#replace nMF_MF as MF_nMF
SI_2020$MF_nMF_Sp12[SI_2020$MF_nMF_Sp12 == "nMF_MF"] <- "MF_nMF"

#calculating mean and sem for SItemp for MF and nMF groups
library(plyr)

cc = ddply(SI_2020, .(MF_nMF_Sp12), summarise,
                                      Mean = mean(SItemp),
                                      SD = sd(SItemp),
                                      sem = SD/ sqrt(length(SItemp)))
cc


#drop NA rows from SIabd column
library(tidyr)
SI_2020_abd = SI_2020 %>% drop_na(SIabd)

dd = ddply(SI_2020_abd, .(MF_nMF_Sp12), summarise,
                                      Mean = mean(SIabd, na.rm = T),
                                      SD = sd(SIabd, na.rm = T),
                                      sem = SD/ sqrt(length(SIabd)))
dd

ccdd = rbind(cc, dd)
write.csv(ccdd, file = "mean_sem for MF and nMF species_2020 data.csv")
```

Calculating similar means for each colour group
```{r}
#calculating mean and sem for SItemp for MF and nMF groups
library(plyr)

ee = ddply(SI_2020, .(Col_grp_Sp12, MF_nMF_Sp12), summarise,
                                      Mean_SItemp = mean(SItemp),
                                      SD = sd(SItemp),
                                      sem = SD/ sqrt(length(SItemp)))
ee


#drop NA rows from SIabd column
library(tidyr)
SI_2020_abd = SI_2020 %>% drop_na(SIabd)

ff = ddply(SI_2020_abd, .(Col_grp_Sp12, MF_nMF_Sp12), summarise,
                                      Mean_SIabd = mean(SIabd, na.rm = T),
                                      SD = sd(SIabd, na.rm = T),
                                      sem = SD/ sqrt(length(SIabd)))
ff

eeff = cbind(ee, ff)
write.csv(eeff, file = "mean_sem for MF_nMF comparisons for colour group combinations_2020 data.csv")
```





